---
title: "EMMA Prototype"
description: Modeling vegetation postfire recovery data
author:
  - name: Adam Wilson & Glenn Moncrieff
date: 10-13-2021
editor_options: 
  chunk_output_type: console
output:
  github_document:
    html_preview: true
---

```{r, echo=F, messages=F, results="hide"}
library(targets)
library(tidyverse)
library(doParallel)
library(raster)
library(lubridate)
library(sf)
# load data saved in the pipeline
tar_load(c(data, stan_data, model_results, spatial_outputs)) 
```

The details are given in [@slingsby_near-real_2020;@wilson_climatic_2015], but in short what we do is estimate the age of a site by calculating the years since the last fire. We then fit a curve to model the recovery of vegetation (measured using NDVI) as a function of it's age. For this we use a negative exponential curve with the following form:

$$\mu_{i,t}=\alpha_i+\gamma_i\Big(1-e^{-\frac{age_{i,t}}{\lambda_i}}\Big)$$

where $\mu_{i,t}$ is the expected NDVI for site $i$ at time $t$

The observed greenness $NDVI_{i,t}$  is assumed to follow a normal distribution with mean $\mu_{i,t}$
$$NDVI_{i,t}\sim\mathcal{N}(\mu_{i,t},\sigma_)$$

An additional level models the parameters of the negative exponential curve as a function of environmental variables. This means that sites with similar environmental conditions should have similar recovery curves. The full model also includes a sinusoidal term to capture seasonal variation, but lets keep it simple here.  

## ADVI

We have `age` in years, a plot identifier `pid`. the observed ndvi `nd` and two plot level environmental variable `env1`, which is mean annual precipitation, and `env2`, which is the summer maximum temperature.  

Lets load up our Stan model which codes the model described above. This is not a particularly clever or efficient way of coding the model, but it is nice and readable and works fine on this example dataset  

## Fitting Overview

### Geographic region



```{r p1, echo=T, eval=T, message=FALSE}
params=c("tau","alpha_mu","gamma_beta","lambda_beta")
posteriors=model_results %>% 
  filter(model_results$parameter%in%params)

ggplot(posteriors,aes(y=parameter, xmin=q5,x=median,xmax=q95))+
  geom_pointrange(fill="grey")
```


## Plot


```{r plot, echo=T, eval=T, message=FALSE}
posterior_summary %>% 
  filter(pid %in% as.numeric(sample(levels(as.factor(posterior_summary$pid)),20))) %>% # just show a few
  ggplot(aes(x=age)) +
 geom_line(aes(y=mean),colour="blue") +
  geom_line(aes(y=ndvi),colour="black",lwd=0.5,alpha=0.3) +
  geom_ribbon(aes(ymin=q5,ymax=q95),alpha=0.5)+
  facet_wrap(~pid) +
#  xlim(c(0,25))+ ylim(c(0,10))+
  labs(x="time since fire (years)",y="NDVI") +
  theme_bw()
```

# Spatial Predictions
This section is not yet working - need to get the coordinates in the original data set.

```{r compare_data2, echo=T, eval=F, message=FALSE}

stan_spatial <- posterior_summary %>% 
  left_join(data,by="cellID") %>% #pid=gsub("[]]","",gsub(".*[[]","",variable))) %>% 
  select(cellID,x,y,date, age,ndvi,mean,q5,q95)


# pred_rast <- foreach(t=sort(unique(stan_spatial$date)),.combine=stack) %do% {
#   stan_spatial %>% 
#     filter(date==t) %>%
#     select(x,y,age,nd,mean,q5) %>% 
#     rasterFromXYZ()
# }

stan_spatial %>% 
  filter(date<as_date("2004-01-01")) %>% 
    ggplot(aes(x=x,y=y,fill=mean))+
    geom_tile()+
    facet_wrap(~date)+
  coord_sf()


```
